%-------------------------
% Resume in Latex
% Author : Shehab Ahmed
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\highlight}[1]{\colorbox{yellow}{#1}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Shehab Eldeen Ahmed Gaber} \\ \vspace{1pt}
    Alexandria, Egypt \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +201210695950 ~ \href{mailto:shehabeldeenahmed727@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shehabeldeenahmed727@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/shehab-ahmed-164bbb244/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Shehab Ahmed}}  ~
    \href{https://github.com/shehab-19}{\raisebox{-0.2\height}\faGithub\ \underline{shehab-19}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Alexandria University}{Sep. 2021 -- May 2026}
      {Third year Electronics and Communication Engineering Undergraduate}{Alexandria, Egypt}
      
      {CGPA: 3.52}
  \resumeSubHeadingListEnd
\vspace{-13pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mind Cloud Robotics}{October 2022 -- Present}
  {Vice Chairman and Software Engineer}{Alexandria University, Egypt}
  \resumeItemListStart
    \resumeItem{Joined MindCloud as a Software Member in the Autonomous Navigation Subteam, responsible for building a comprehensive navigation system integrating GPS, IMU, LIDAR, and encoder sensors using ROS.}
    \resumeItem{Achieved third place at UGVC2023 competition.}
    \resumeItem{Promoted to Software Mentor, leading the development of new systems and enhancements to existing projects.}
    \resumeItem{Achieved second place at UGVC2024 competition and promoted to Vice Chairman, leading the team to further successes and achievements.}
  \resumeItemListEnd

\resumeSubheading
  {\textbf{\href{https://drive.google.com/file/d/1Dm58e-RYl9d5-UyJLDb2hoioJ44owtN_/view?usp=drive_link}{National Telecommunication Institute (NTI)}}}{Aug. 2024 -- Sep. 2024}
  {AWS Cloud Internship Trainee}{Alexandria, Egypt}
  \resumeItemListStart
    \resumeItem{Completed an intensive one-month program, gaining expertise in key concepts and practical applications of AWS Cloud.}
  \resumeItemListEnd


\resumeSubheading
  {Digital Egypt Pioneers Initiative (DEPI)}{Oct. 2024 -- Present}
  {DevOps Trainee}{Alexandria, Egypt}
  \resumeItemListStart
    \resumeItem{Joined the DevOps Engineer program, acquiring real-world experience and hands-on skills in DevOps Engineering.}
  \resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

     \resumeProjectHeading
           {\textbf{\href{https://github.com/shehab-19/frontend-app-deployment}{Front-End App Deployment Project}} {\faExternalLink}$|$ \emph{Docker, Jenkins}}{2024}
          \resumeItemListStart
            \resumeItem{Developed an automated deployment pipeline for a Node.js front-end application using Jenkins and Docker.}
          \resumeItemListEnd
           \vspace{-13pt}
    
      \resumeProjectHeading       
      {\textbf{A complete Autonomous Navigation System}  $|$ \emph{Python, OOP, ROS, IMU, LIDAR, Encoder, GPS}}{2023}
          \resumeItemListStart
            \resumeItem{Developed a multipoint obstacle avoidance autonomous navigation system on a ground rover using ROS and  IMU, LIDAR, Encoder and GPS sensors at MINDCLOUD Robotics.}
          \resumeItemListEnd
          \vspace{-13pt}
          
    \resumeProjectHeading
           {\textbf{\href{https://github.com/shehab-19/C_Projects}{C problem solving}} {\faExternalLink}$|$ \emph{C}}{2023}
          \resumeItemListStart
            \resumeItem{Solved UVA problems using C language.}
          \resumeItemListEnd
           \vspace{-13pt}
    
      \resumeProjectHeading
        {\textbf{\href{https://github.com/shehab-19/Flutter-mobile-application-controlling-an-RGB}{Flutter Application to control an RGB}} {\faExternalLink} $|$ \emph{flutter, ESP8266}}{2024}
          \resumeItemListStart
            \resumeItem{Created a flutter application using Dart and VS code including a brightness bar and buttons for controlling the color.}
            \resumeItem{Linked the ESP8266 code with my flutter app using the ESP WIFI module and ran the app on the web and the mobile successfully.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{\href{https://github.com/shehab-19/matlab-labs-and-projects}{Matlab Projects}} {\faExternalLink} $|$ \emph{Matlab, appdesigner}}{2024}
          \resumeItemListStart
            \resumeItem{Developed numerous MATLAB labs and projects, including a signal generator, sound communication system, and a power systems project with a GUI.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------AWARDS AND CERTIFICATES-----------
\section{Awards and Certificates}
  \resumeSubHeadingListStart
\resumeSubheading
      {Second place UGVC achiever}{July 2024}    {\href{https://drive.google.com/file/d/1cFxavxoD6v_c5iXHRh9SJqUTRxFyyfvN/view?usp=drive_link}{\underline{Military Technical College}} \faExternalLink}{Cairo, Egypt}   
    \resumeSubheading
      {Third place UGVC achiever}{July 2023}
      {\href{https://drive.google.com/file/d/1zf9sWT-c8BKFh4U4YXXCVKA7WTfY0kZO/view}{\underline{Military Technical College}} \faExternalLink}{Cairo, Egypt}
    \resumeSubheading
    {ETISAL/SIEMENS Automotive Internship}{2023}     {\href{https://drive.google.com/file/d/1rIcjcuHYTnsQna63ZekfH8VYNT9ynNfg/view}{\underline{ETISAL/SIEMENS}} \faExternalLink}{Alexandria, Egypt}
    \resumeSubheading
      {ZEWAIL AI training}{2023} {\href{https://drive.google.com/file/d/1rCjUHT6S1Zl9ZXPRAIWheJSxOMV4waIb/view?pli=1}{\underline{ZEWAIL CITY}} \faExternalLink}{Cairo, Egypt}

      \resumeSubheading
      {WEPCO Summer Training}{2023}      {\href{https://drive.google.com/file/d/1NS0sT6UOV6XFCg1TI2ExFUzumy8VKVEe/view}{\underline{WEPCO}} \faExternalLink}{Alexandria, Egypt}
      
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, C++, Dart, VHDL, Matlab, OOP, Data structures, Algorithms} \\
     \textbf{Technologies/Frameworks}{: Linux, Docker, Terraform, Jenkins, CI/CD, ROS, GitHub, AWS } \\
    }}
 \end{itemize}
 \vspace{-10pt}


%-----------INVOLVEMENT---------------
\section{Organizations}
    \resumeSubHeadingListStart
        \resumeSubheading{Mind Utopia}{2023}{Training and Development Staff Member}{Alexandria University}
            \resumeItemListStart
                \resumeItem{Enhanced communication, presentation, and leadership skills.}
                \resumeItem{Led a team to mentor and train in presentation technique}
            \resumeItemListEnd

        \resumeSubheading{SMU}{2023 -- Present}{Projects and Planning committee Staff Member}{Alexandria University}
            \resumeItemListStart
                \resumeItem{Actively engaged in preparing and delivering professional presentations.}
                \resumeItem{Participated and prepared for various university events}
            \resumeItemListEnd

          \resumeSubheading{IEEE SSCS}{2023 -- Present}{Public Relations Staff Member}{Alexandria University}
            \resumeItemListStart
                \resumeItem{Trained in PR with skills in creating and negotiating professional proposals.}
                \resumeItem{Trained in conducting effective negotiations and closing successful business deals.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Arabic}{: Native} \\
     \textbf{English}{: High professional fluency}
    }}
 \end{itemize}
 \vspace{-10pt}
 
\end{document}
